\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{graphicx}

\title{Software Design Specification}
\author{Your Name or Team}
\date{Version 1.0 \\\ \today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction}
\subsection{Purpose}
Define the purpose of this document, its intended audience, and how it should be used.

\subsection{Scope}
Describe the scope of the software design, including system name and any relevant version or model numbers.

\subsection{Definitions, Acronyms, and Abbreviations}
Explain the terms, acronyms, and abbreviations used in this document.

\subsection{References}
Provide a complete list of documents referenced elsewhere in the document.

\subsection{Overview}
Briefly summarize the rest of the document.

\section{System Overview}
Provide a general description of the system including its functionality and matters related to the overall system and its design.

\section{System Architecture}
\subsection{Architectural Design}
Describe the software’s architecture, referencing any major frameworks or methodologies used.

\subsection{Decomposition Description}
Detail the breakdown of the software’s architecture, if applicable.

\subsection{Design Rationale}
Explain the reasons behind the chosen architectural and design approaches.

\section{Data Design}
\subsection{Database Description}
Detail the database design, structure, and any related data management systems.

\subsection{Data Structures}
Describe any data structures used in the system and their relationships.

\section{Component Design}
Detail the design of the software components, including their responsibilities and interactions.

\section{Interface Design}
\subsection{External Interfaces}
Detail the design of external interface connections, protocols, and standards.

\subsection{User Interfaces}
Describe the design of the user interface, including screen layouts and user interaction flows.

\section{Dynamic System Design}
Explain the dynamic processes, activities, and tasks within the system, including any state diagrams or sequence diagrams.

\section{Non-Functional Requirements}
Detail the design considerations for non-functional requirements, including performance, security, and reliability constraints.

\appendix
\section{Appendix A: Glossary}
\section{Appendix B: Feasibility Study}
\section{Appendix C: Issue Log}

\end{document}
